A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-15 paper/ms.tex
added a todo
parens

% to-do list
% ----------
% - add items here

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright solar-type
  stars, HD 240429 and HD 240430, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial $|\Delta \bs{x}| < XX~\pc$ at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocity vectors
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high signal-to-noise radial-velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that these were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of high
  condensation-temperature elements of the two stars are very different,
  challenging this simple picture.
  We consider formation scenarios in which the pair either (1) formed together
  with identical abundances but later accreted very different quantities of
  protoplantary, rocky material, (2) were born together but with very different
  metal abundances, or (3) interacted with a field star or binary and exchanged
  a member.
  We favor scenario (1), in which the star HD 240430 consumed $\approx$10's of
  Earth masses of rocky material in small units (many rocky bodies rather than
  a few giant planets).
  Direct-imaging and precision radial-velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}

>>>>

% to-do list
% ----------
% - Add references and uncertainties to Table 1

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright solar-type
  stars, HD 240429 and HD 240430, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial ($|\Delta \bs{x}| < XX~\pc$) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocity vectors
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high signal-to-noise radial-velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that these were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of high
  condensation-temperature elements of the two stars are very different,
  challenging this simple picture.
  We consider formation scenarios in which the pair either (1) formed together
  with identical abundances but later accreted very different quantities of
  protoplantary, rocky material, (2) were born together but with very different
  metal abundances, or (3) interacted with a field star or binary and exchanged
  a member.
  We favor scenario (1), in which the star HD 240430 consumed $\approx$10's of
  Earth masses of rocky material in small units (many rocky bodies rather than
  a few giant planets).
  Direct-imaging and precision radial-velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}
